---
title: "time_series"
author: "jb"
date: "5/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(urca)
library(fpp)
library(tidyverse)
library(radiant)
library(dynlm)
```

## Methodology

__Method 1__
Objective: Create a predictive model for one movie given similar movie.

1. Filter for top 20 similar movies for one movie

2. Hold out is movie of choice. Train is 20 other most similar movies.

3. Use a dynamic regressive model to predict

4. Calculate RMSE 

### Load Data
```{r}
rollup_1k_insta <- read_tsv('data/view_brand_rollup_instagram_1k-10k.tsv', guess_max = 100000)
rollup_1k_fb <- read_tsv('data/view_brand_rollup_facebook_1k-10k.tsv', guess_max = 100000)
rollup_1k_twit <- read_tsv('data/view_brand_rollup_twitter_1k-10k.tsv', guess_max = 100000)

rollup_10k_insta <- read_tsv('data/view_brand_rollup_instagram_10kplus.tsv', guess_max = 100000)
rollup_10k_fb <- read_tsv('data/view_brand_rollup_facebook_10kplus.tsv', guess_max = 100000)
rollup_10k_twit <- read_tsv('data/view_brand_rollup_twitter_10kplus.tsv', guess_max = 100000)

brand_1k <- read_tsv('data/brand_source_affiliations_1k-10k.tsv')


movies <- read_csv('data_concat/brands_with_extras.csv')
colnames(movies)[2] <- 'brand_ods_id'

movies <- movies %>%
  mutate(budget_quant = factor(xtile(budget, 5, T))) 

#days_after_release category
rollup_fb <- rollup_1k_fb %>%
  rbind(rollup_10k_fb) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

rollup_insta <- rollup_1k_insta %>%
  rbind(rollup_10k_insta) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

rollup_twit <- rollup_1k_twit %>%
  rbind(rollup_10k_twit) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

ts_fb <- rollup_fb %>%
  filter(between(days_after_release, -365, 0)) %>%
  mutate(avg_interactions_per_post = total_post_interactions/total_post,
         days_after_release = days_after_release + 365)

ts_insta <- rollup_insta %>%
  filter(between(days_after_release, -365, 0)) %>%
  mutate(days_after_release = days_after_release + 365)

ts_twit <- rollup_fb %>%
  filter(between(days_after_release, -365, 0)) %>%
  mutate(avg_interactions_per_post = total_post_interactions/total_post,
         days_after_release = days_after_release + 365)
```


## Method 1
### 1. Filter and split
1. Filter for top 20 similar movies for one movie

2. Hold out is movie of choice. Train is 10 other most similar movies.
```{r}
jac <- read_csv('data_concat/jac_sim_all_genres.csv')

top20 <- jac[, 1:2] %>%
  arrange(desc(`Blade Runner 2049`)) %>%
  slice(2:11) %>%
  select(replace) %>%
  unlist()

### Facebook
df_fb <- ts_fb %>%
  filter(replace %in% top20) %>%
  select(replace, movie_id, total_post_interactions, days_after_release) 

selected_movie_fb <- ts_fb %>%
  filter(replace == 'Blade Runner 2049')%>%
  select(replace, movie_id, total_post_interactions, days_after_release)



### Instagram
df_insta <- ts_insta %>%
  filter(replace %in% top20) %>%
  select(replace, movie_id, total_post_interactions, days_after_release)

selected_movie_insta <- ts_insta %>%
  filter(replace == 'Blade Runner 2049')%>%
  select(replace, movie_id, total_post_interactions, days_after_release)


  
### Twitter
df_twit <- ts_twit %>%
  filter(replace %in% top20) %>%
  select(replace, movie_id, total_post_interactions, days_after_release) 

selected_movie_twit <- ts_twit %>%
  filter(replace == 'Blade Runner 2049')%>%
  select(replace, movie_id, total_post_interactions, days_after_release)

```

### 2. Predicting
3. Use a dynamic regressive model to predict

__Facebook__
Visualising data first
```{r}
df_fb %>%
  ggplot(aes(days_after_release, total_post_interactions, color = replace)) +
  geom_line()
```


```{r}
top_names <- unique(df_fb$replace)

auto_ts <- function(df, top_names, n, start, end) {
  x <- df %>%
    filter(replace == top_names[n])
  
  ts <- ts(x$total_post_interactions, start = x$days_after_release)
  
  ts <- window(ts, start = start, end = end)
  
  return(ts)
}


ts_select <- ts(selected_movie_fb$total_post_interactions, start = selected_movie_fb$days_after_release)

data <- cbind(auto_ts(df_fb, top_names, 1), auto_ts(df_fb, top_names, 2), auto_ts(df_fb, top_names, 3))

model <- dynlm(auto_ts(df_fb, top_names, 1) ~ 
                 auto_ts(df_fb, top_names, 2) +
                 auto_ts(df_fb, top_names, 3) +
                 auto_ts(df_fb, top_names, 4) +
                 auto_ts(df_fb, top_names, 5) +
                 auto_ts(df_fb, top_names, 6) +
                 auto_ts(df_fb, top_names, 7) + 
                 auto_ts(df_fb, top_names, 8) +
                 auto_ts(df_fb, top_names, 9) +
                 auto_ts(df_fb, top_names, 10))

pred <- predict(model, ts_select)

accuracy(pred, ts_select)

autoplot(ts_select, series = 'original') + 
  autolayer(ts(pred), series = 'prediction')
```


Try different forecasting methods by subsetting data.
__100 days before__
```{r}
test_100 <- window(ts_select, start = 266) 

train_100 <- window(ts_select, end = 265)

# Holt's Model
fit1 <- holt(train_100, h= 100)

autoplot(test_100, series = 'actual') +
  autolayer(fit1, h = 100, PI = FALSE, series = 'prediction')

# Arima
fit2 <- auto.arima(train_100)

autoplot(test_100, series = 'actual') +
  autolayer(forecast(fit2, h = 100), PI = FALSE, series = 'prediction')


accuracy(fit1, test_100)
accuracy(forecast(fit2, h=100), test_100)
```

```{r}
x <- df_fb %>%
    group_by(days_after_release) %>%
    summarize(avg_posts = mean(total_post_interactions))

x <- ts(data = x$avg_posts, start = x$days_after_release)

x_100 <- window(x, end = 265)

fit3 <- auto.arima(x_100)

accuracy(forecast(fit2, h=100), test_100)

autoplot(test_100, series = 'actual') +
  autolayer(forecast(fit3, h = 100), PI = FALSE, series = 'prediction')
```


## Dynamic Model
```{r}
model <- dynlm(auto_ts(df_fb, top_names, 1, 0, end = 265) ~ 
                 auto_ts(df_fb, top_names, 2, 0, end = 265) +
                 auto_ts(df_fb, top_names, 3, 0, end = 265) +
                 auto_ts(df_fb, top_names, 4, 0, end = 265) +
                 auto_ts(df_fb, top_names, 5, 0, end = 265) +
                 auto_ts(df_fb, top_names, 6, 0, end = 265) +
                 auto_ts(df_fb, top_names, 7, 0, end = 265) + 
                 auto_ts(df_fb, top_names, 8, 0, end = 265) +
                 auto_ts(df_fb, top_names, 9, 0, end = 265) +
                 auto_ts(df_fb, top_names, 10, 0, end = 265))


pred <- predict(model, train_100)

accuracy(pred, test_100)

autoplot(ts_select, series = 'original') + 
  autolayer(ts(pred), series = 'prediction')
```