---
title: "Exploratory Analysis"
author: "jb"
date: "4/17/2020"
output: html_document
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(radiant)
library(readr)
```

```{r load, message = FALSE, warning = FALSE}
rollup_1k_insta <- read_tsv('data/view_brand_rollup_instagram_1k-10k.tsv', guess_max = 100000)
rollup_1k_fb <- read_tsv('data/view_brand_rollup_facebook_1k-10k.tsv', guess_max = 100000)
rollup_1k_twit <- read_tsv('data/view_brand_rollup_twitter_1k-10k.tsv', guess_max = 100000)

rollup_10k_insta <- read_tsv('data/view_brand_rollup_instagram_10kplus.tsv', guess_max = 100000)
rollup_10k_fb <- read_tsv('data/view_brand_rollup_facebook_10kplus.tsv', guess_max = 100000)
rollup_10k_twit <- read_tsv('data/view_brand_rollup_twitter_10kplus.tsv', guess_max = 100000)

brand_1k <- read_tsv('data/brand_source_affiliations_1k-10k.tsv')


comments_1k <- read_tsv('data/comments_1k-10k.tsv', col_names = FALSE)
colnames(comments_1k) <- c('comment_id',	'comment_dcs_uid',	'comment_author_id',	'post_dcs_uid',	'post_author_dcs_uid',	'comment_lfm_type',	'comment_posted_at',	'comment_message', 'comment_sentiment_polarity',	'comment_primary_emotion',	'comment_ace_metadata',	'topics',	'comment_is_quote',	'spec_channel')

#movies <- read_csv('data_concat/brands_with_extras.csv')
brands_with_extras <- read_csv("data_concat/brands_with_extras.csv")
movies <- brands_with_extras
colnames(movies)[2] <- 'brand_ods_id'
```


```{r}

```

Concerns:
Uncertain if movies are randomly sampled out of database. Even if we split the dataset to budget quantiles, might not be representative.  

## Creating Filters and Transforming Data
```{r}
movies <- movies %>%
  mutate(budget_quant = factor(xtile(budget, 5, T))) 

#days_after_release category
rollup_fb <- rollup_1k_fb %>%
  rbind(rollup_10k_fb) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

rollup_insta <- rollup_1k_insta %>%
  rbind(rollup_10k_insta) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

rollup_twit <- rollup_1k_twit %>%
  rbind(rollup_10k_twit) %>%
  left_join(movies, by = c('movie_id' = 'brand_ods_id')) %>%
  mutate(
      days_after_release = data_for - released_on)

```


============================================= General =================================================

## 1. General Trends
__Facebook__
```{r}  
# Likes
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_likes = mean(likes, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_likes)) +
  geom_vline(aes(xintercept = 0), color = '#FFAB40') +
  theme_minimal()


# Engagement
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_engagement = mean(engagement_rate, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_engagement)) +
  theme_minimal()


# Interactions
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions)) +
  theme_minimal() +
  geom_vline(aes(xintercept = 0), color = 'blue')
```

__Instagram__
```{r}
# Likes
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_likes = mean(total_likes, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_likes))

# Comments
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_comments = mean(total_comments, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_comments))

# Interactions
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_comments = mean(total_comments, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_comments))

```


__Twitter__
```{r}
# Retweets
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_retweets = mean(total_retweets, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_retweets))

# Favorites
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_favorites = mean(total_favorites, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_favorites))

# Replies
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_replies = mean(total_replies, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_replies))

# Interactions
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions))

```


=========================================== Drilldown =================================================

## 1. Budget
__Facebook__
```{r warning = FALSE}  
# Likes
rollup_fb %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_likes = mean(likes, na.rm = T)) %>%
  ggplot () +
  geom_point(aes(days_after_release, mean_likes, color = budget_quant)) +
  geom_vline(aes(xintercept = 0), color = 'blue')


# Engagement
rollup_fb %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_engagement = mean(engagement_rate, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_engagement, color = budget_quant)) + 
  facet_wrap(~budget_quant) +
  geom_vline(aes(xintercept = 0), color = 'blue')


# Interactions
rollup_fb %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = budget_quant)) +
  geom_vline(aes(xintercept = 0), color = 'blue')
```


__Instagram__
```{r warning = FALSE}
# Likes
rollup_insta %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_likes = mean(total_likes, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_likes, color = budget_quant)) +
  geom_vline(aes(xintercept = 0), color = 'blue')

# Comments
rollup_insta %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_comments = mean(total_comments, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_comments, color = budget_quant)) + 
  geom_vline(aes(xintercept = 0), color = 'blue')

# Interactions
rollup_insta %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = budget_quant)) +
  geom_vline(aes(xintercept = 0), color = 'blue')

```

__Twitter__
```{r warning = FALSE}
# Retweets
rollup_twit %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_retweets = mean(total_retweets, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_retweets, color = budget_quant)) + 
  geom_vline(aes(xintercept = 0), color = 'blue')
 

# Favorites
rollup_twit %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_favorites = mean(total_favorites, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_favorites, color = budget_quant)) + 
  geom_vline(aes(xintercept = 0), color = 'blue')


# Replies
rollup_twit %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_replies = mean(total_replies, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_replies, color = budget_quant)) + 
  geom_vline(aes(xintercept = 0), color = 'blue')


# Interactions
rollup_twit %>%
  filter(between(days_after_release, -365, 365) & !is.na(budget)) %>%
  group_by(days_after_release, budget_quant) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = budget_quant)) + 
  geom_vline(aes(xintercept = 0), color = 'blue')

```



## 2. Genre
__Facebook__
```{r warning = FALSE}  
# Likes
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_likes = mean(likes, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_likes, color = top_genre)) +
  geom_vline(aes(xintercept = 0), color = 'blue') + 
  facet_wrap(~top_genre)


# Engagement
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_engagement = mean(engagement_rate, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_engagement, color = top_genre)) + 
  facet_wrap(~top_genre) +
  geom_vline(aes(xintercept = 0), color = 'blue')


# Interactions
rollup_fb %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = top_genre)) +
  geom_vline(aes(xintercept = 0), color = 'blue') +
  facet_wrap(~top_genre)
```


__Instagram__
```{r warning = FALSE}
# Likes
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_likes = mean(total_likes, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_likes, color = top_genre)) +
  geom_vline(aes(xintercept = 0), color = 'blue') +
  facet_wrap(~top_genre)

# Comments
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_comments = mean(total_comments, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_comments, color = top_genre)) +
  geom_vline(aes(xintercept = 0), color = 'blue') +
  facet_wrap(~top_genre)


# Interactions
rollup_insta %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = top_genre)) +
  geom_vline(aes(xintercept = 0), color = 'blue') +
  facet_wrap(~top_genre)

```


__Twitter__
```{r warning = FALSE}
# Retweets
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_retweets = mean(total_retweets, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_retweets, color = top_genre)) + 
  geom_vline(aes(xintercept = 0), color = 'blue') + 
  facet_wrap(~top_genre)
 

# Favorites
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_favorites = mean(total_favorites, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_favorites, color = top_genre)) + 
  geom_vline(aes(xintercept = 0), color = 'blue') + 
  facet_wrap(~top_genre)


# Replies
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_replies = mean(total_replies, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_replies, color = top_genre)) + 
  geom_vline(aes(xintercept = 0), color = 'blue') + 
  facet_wrap(~top_genre)


# Interactions
rollup_twit %>%
  filter(between(days_after_release, -365, 365)) %>%
  group_by(days_after_release, top_genre) %>%
  summarize(mean_interactions = mean(total_post_interactions, na.rm = T)) %>%
  ggplot() +
  geom_point(aes(days_after_release, mean_interactions, color = top_genre)) + 
  geom_vline(aes(xintercept = 0), color = 'blue') + 
  facet_wrap(~top_genre)


```


========================================= Random Movies ===============================================
## Drill Down
### a. By Budget
__Facebook__
```{r}
## Likes
rollup_fb %>%
  filter(!is.na(budget)) %>%
  group_by(movie_id) %>%
  mutate(max_likes = max(likes, na.rm = T)) %>%
  ungroup() %>%
  group_by(budget_quant) %>%
  summarize(
      mean_likes = mean(max_likes),
      sd_likes = sd(max_likes)
  )

# x <- rollup_fb %>%
#   filter(!is.na(budget)) %>%
#   group_by(movie_id) %>%
#   mutate(max_likes = max(likes, na.rm = T)) %>%
#   group_by(movie_id) %>%
#   summarize(likes = mean(max_likes),
#             budget = mean(budget))

rollup_fb %>%
  filter(!is.na(budget)) %>%
  group_by(movie_id) %>%
  mutate(max_likes = max(likes, na.rm = T)) %>%
  group_by(movie_id) %>%
  summarize(likes = mean(max_likes),
            budget = mean(budget)) %>%
  ggplot() +
  geom_point(aes(budget, likes))
  

## Engagement
rollup_fb %>%
  filter(!is.na(budget)) %>%
  group_by(movie_id) %>%
  mutate(max_engagement = max(engagement_rate, na.rm = T)) %>%
  ungroup() %>%
  group_by(budget_quant) %>%
  summarize(
      mean_engagement = mean(max_engagement),
      sd_engagement = sd(max_engagement)
  )

```



